\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[2]{\noindent\textbf{Name: #1}\hfill \textbf{Section: #2}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[2ex]
 \textbf{Signature:} \underline{\hspace*{8cm}} }
 
\newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{compactitem}[$\Box$] 
\item Did you type in your name and section? 
\item Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc.\ that you have consulted)
\item Did you sign that you followed the Aggie honor code? 
\item Did you solve all problems? 
\item Did you submit both the .tex and .pdf files of your homework separately 
to the correct link on eCampus?
\item Did you submit a signed hardcopy of the pdf file in class? 
\end{compactitem}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[2]{\begin{quote}\textbf{Due dates:} Electronic
    submission of \textsl{yourLastName-yourFirstName-hw9.tex} and 
    \textsl{yourLastName-yourFirstName-hw9.pdf} files of this homework is due on
    \textbf{#1} on \texttt{http://ecampus.tamu.edu}. You will see two separate links
    to turn in the .tex file and the .pdf file separately. Please do not archive or compress the files.  
    A signed paper copy of the pdf file is due on \textbf{#2} at the beginning of class.
    \textbf{If any of the three submissions are missing, your work will not be graded.}
    \textbf{Late submissions of any form will not be accepted.}\end{quote} }

\newcommand{\N}{\mathbf{N}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Z}{\mathbf{Z}}


\begin{document}
\vspace*{-18mm}
\begin{center}
{\large
CSCE 222 [Sections 502, 503] Discrete Structures for Computing\\[.5ex]
Spring 2017 -- Hyunyoung Lee\\}
\end{center}
\problemset{9}
\duedate{Wednesday, 4/19/2017 \textit{before} the beginning of class}{Wednesday, 4/19/2017}
\name{ (type your name here)}{(type your section here)}
\begin{resources} (All people, books, articles, web pages, etc.\ that
  have been consulted when producing your answers to this homework)
\end{resources}
\honor

\begin{problem} (16 points)
Section 9.1, Exercise 6, page 581
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
We define on the set $\N_1=\{1,2,3,\cdots\}$ of positive integers a
relation $\sim$ such that two positive integers $x$ and $y$ satisfy
$x\sim y$ if and only if $x/y=2^k$ for some integer $k$. 
Show that $\sim$ is an equivalence relation.
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
Section 9.5, Exercise 2, page 615
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
Section 9.5, Exercise 16, page 615
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
Section 9.5, Exercise 58, page 618
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
Section 9.6, Exercise 4, page 630
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (10 points)
Section 9.6, Exercise 16, page 630.
\ \\
You can answer the subproblem c) by either actually drawing the Hasse diagram 
or by clearly writing out the cover relation of the Hasse diagram instead of 
drawing the diagram.
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} ($8+8\times 2 = 24$ points)
Section 9.6, Exercise 34, page 631.
\ \\ 
First, draw the Hasse diagram or clearly write out the cover relation.  This
part is worth eight points.  Each of the eight subproblems is worth two points.
For subproblems c) and d), if it exists, give the number.
\end{problem}
\begin{solution} 
\end{solution}

\goodbreak
\checklist
\end{document}
